---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {
  color: Blue;
}
```

## Uber Eats Delivery Tracker

This report shows trends from my Uber Eats orders (24 total) between March 26 and April 2, 2025.

## What is the delivery time?

```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRESDrweB7n55EdzKdF6UJ71c5i1-VrxLFLWK8gl1wZ3HJ75okT3YhjFLxTrGXUjs4UssSp1lldBjzw/pub?output=csv")

latest_data <- logged_data %>%
    rename(
      timestamp = "Timestamp",
      delivery_time = "How many minutes did the delivery take from order confirmation to arrival?",
      food_category = "What category best describes the food you ordered?",
      cost = "What was the total order cost (in dollars, excluding tip and delivery fees)?"
    )


plot2 <- latest_data %>%
  group_by(food_category) %>%
  summarise(average_delivery = mean(delivery_time, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(x = food_category, y = average_delivery), stat = "identity", fill = "lightblue") +
  labs(
    title = "Average Delivery Time by Food Category",
    x = "Food Category",
    y = "Average Delivery Time (minutes)")
plot2
```

# Summary of delivery time on different food
The Average delivery time is 24.5 minutes, Italian food has the longest average delivery time about 30 minutes; other category is about the same around 21 to 25 minutes.

## How much did I spend?

```{r}

plot3 <- latest_data %>%
  group_by(food_category) %>%
  summarise(total_cost = sum(cost, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(x = food_category, y = total_cost), stat = "identity", fill = "lightgreen") +
  labs(
    title = "Total Food Cost by Food Category",
    x = "Food Category",
    y = "Total Food Cost ($)")
plot3

plot1 <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = food_category), fill = "orange") +
  labs(
    title = "Number of Orders by Food Category",
    x = "Food Category",
    y = "Number of Orders")
plot1
```

# Summary of the money I spend on
The total food costs is 570 dollars (very expensive), Fast food is the most expensive and is twice as much as Asian and italian food, dessert is the cheapest. I order same amount of times for Asian and Fast Food, same amount of times for dessert and italian. We can say I spend twice as much as money on Fast food than Asian food and twice as much as money on italian than dessert.


