---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
h2 {
  color: Blue;
}
```

## Uber Eats Delivery Tracker

This report shows trends from my Uber Eats orders.

## Number of Orders
```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRESDrweB7n55EdzKdF6UJ71c5i1-VrxLFLWK8gl1wZ3HJ75okT3YhjFLxTrGXUjs4UssSp1lldBjzw/pub?output=csv")

latest_data <- logged_data %>%
    rename(
      timestamp = "Timestamp",
      delivery_time = "How many minutes did the delivery take from order confirmation to arrival?",
      food_category = "What category best describes the food you ordered?",
      cost = "What was the total order cost (in dollars, excluding tip and delivery fees)?"
    )

plot1 <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = food_category), fill = "orange") +
  labs(
    title = "Number of Orders by Food Category",
    x = "Food Category",
    y = "Number of Orders")
plot1

category_counts <- latest_data %>%
  group_by(food_category) %>%
  summarise(count = n())

```

# Number of Orders by Food Category

Here is the number of orders by food category 
```{r}
knitr::kable(category_counts, col.names = c("Food Category", "Number of Orders"))
```
## What is the delivery time?

```{r}



plot2 <- latest_data %>%
  group_by(food_category) %>%
  summarise(average_delivery = mean(delivery_time, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(x = food_category, y = average_delivery), stat = "identity", fill = "lightblue") +
  labs(
    title = "Average Delivery Time by Food Category",
    x = "Food Category",
    y = "Average Delivery Time (minutes)")
plot2
```


```{r}
average_delivery <- mean(latest_data$delivery_time, na.rm = TRUE)
```
# The Average delivery time
My orders took an average of `r round(average_delivery, 1)` minutes to deliver

## How much did I spend?

```{r}

plot3 <- latest_data %>%
  group_by(food_category) %>%
  summarise(total_cost = sum(cost, na.rm = TRUE)) %>%
  ggplot() +
  geom_bar(aes(x = food_category, y = total_cost), stat = "identity", fill = "lightgreen") +
  labs(
    title = "Total Food Cost by Food Category",
    x = "Food Category",
    y = "Total Food Cost ($)")
plot3

mean_cost <- mean(latest_data$cost, na.rm = TRUE)
total_cost <- sum(latest_data$cost, na.rm = TRUE)
```

# Summary of the money I spend on
I spend  `r round(total_cost, 2)` dollars total and average `r round(mean_cost, 2)` dollars on uber eats


